Hydra Battles and Cie

### 2021-07-24 doc/chapter-primrec.tex
more snippets

\begin{Coqsrc}
Lemma plusIsPR : isPR 2 plus.
Proof.
  apply isPR_extEqual_trans with plus_alt.
  - unfold plus_alt; apply ind1ParamIsPR.
\end{Coqsrc}

\begin{Coqanswer}
2 subgoals (ID 126)

  ============================
  isPR 3 (fun _ y _ : nat => S y)

subgoal 2 (ID 127) is:
 isPR 1 (fun b : nat => b)
\end{Coqanswer}

@@

@@

The following proof decomposes the \texttt{double} function as the composition of 
multiplication with the identity and the constant function which returns $2$.
\emph{Note that the lemma \texttt{const1\_NIsPR} considers this function as an unary function (unlike \texttt{const0\_NIsPR})}. 
\input{movies/snippets/PrimRecExamples/doubleIsPRa}
\input{movies/snippets/PrimRecExamples/doubleIsPRb}

@@

\begin{Coqsrc}
Fixpoint fact n :=
  match n with 
          | 0 => 1
          | S p  => n * fact p
  end.

Fixpoint exp n p :=
  match p with
  | 0 => 1
  | S m =>  exp n m * n
  end.

Fixpoint tower2 n :=
  match n with
  | 0 => 1
  | S p => exp 2 (tower2 p)
  end.
\end{Coqsrc}

@@

\begin{Coqsrc}
Fixpoint fib (n:nat) : nat :=
  match n with
  | 0 => 1
  | 1 => 1
  | S ((S p) as q) => fib q + fib p
  end.
\end{Coqsrc}

@@

\index{primrec}{Exercises}
\begin{exercise}
Prove the following lemmas (which may help to solve the next  exercise).

\begin{Coqsrc}
Lemma boundedSearch3 (P: naryRel 2) (b  : nat), 
    boundedSearch P b <= b.

Lemma boundedSearch4 (P: naryRel 2) (b  : nat):
  P b b = true -> P b (boundedSearch P b) = true.
\end{Coqsrc}
\end{exercise}

>>>>

@@

%\input{movies/snippets/PrimRecExamples/justATest}

@@

The following proof decomposes the \texttt{double} function as the composition of 
multiplication with the identity and the constant function which returns $2$.
\emph{Note that the lemma \texttt{const1\_NIsPR} considers this function as an unary function (unlike \texttt{const0\_NIsPR})}. 
\input{movies/snippets/PrimRecExamples/doubleIsPRa}

@@

\input{movies/snippets/MorePRExamples/factDef}

\input{movies/snippets/MorePRExamples/expDef}

\input{movies/snippets/MorePRExamples/tower2Def}

@@

\input{movies/snippets/FibonacciPR/fibDef}

@@

\index{primrec}{Exercises}
\begin{exercise}

Prove the following lemmas (which may help to solve the next  exercise).

\input{movies/snippets/isqrt/boundedSearch3}
\input{movies/snippets/isqrt/boundedSearch4}

\textbf{Note:}  The function \texttt{boundedSearch} is defined
in Library \href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec}. 
\end{exercise}
